Higher-Order unification for free!

### 2024-04-15 paper/main.tex
todos
add todo

\begin{theorem}[Fidelity in \maybeeta]
  % F x = z, F x y = z y
  Given a list of unification problems \foUnifPb, if \noteD{riprendere sec 3.1}
  $\forall t, t\in\subterm{\foUnifPb} \Rightarrow t \notin \notllambda$ and if the 
  memory map is bijective, then
  the introduction 
  of \linketa guarantees \fullref{prop:fidelity}.
  \footnote{This premise is fulfilled in \cref{sec:invariant1}}
  \label{lemma:fidelity-maybeeta}
\end{theorem}

@@

\begin{theorem}[Fidelity with \linkbeta]
  The introduction of \linkbeta guarantees \fullref{prop:fidelity-recovery}
  if \Uo{} fails outside \llambda.
\end{theorem}

@@

\emph{The approach presented in this paper}
provides a third option that addresses all the concerns
mentioned earlier. It capitalizes on the benefit of not requiring to fully
implement
the unification algorithm of the object language. Instead, it employs the
unification capabilities of the meta language, facilitated by the various links
%we establish
to manage ``problematic'' subterms. As a result of this choice our encoding takes
advantage of indexing data structures and mode analysis for clause filtering.
It it worth mentioning that we only replace terms with variables only
when it is strictly needed, leaving the rest of the term structure intact
and hence indexable by the meta language logic programming engine.
Moreover, the unification process we obtain is ready to take
advantage of potential improvements to the programming engine,
such as tabled search, and apply forms of static analysis for
the meta language, such as determinacy, to the object language. 
Finally, our approach is flexible enough to accommodate different strategies
and heuristics to handle terms outside the pattern fragment, and
it is not tightly coupled with CIC.

>>>>

\begin{theorem}[Fidelity in \maybeeta]
  % F x = z, F x y = z y
  Given a list of unification problems \foUnifPb, if \noteD{riprendere sec 3.1}
  $\forall t, t\in\subterm{\foUnifPb} \Rightarrow t \notin \notllambda$ and if the 
  memory map is bijective, then
  the introduction 
  of \linketa guarantees \fullref{prop:fidelity}.
  \footnote{This premise is fulfilled in \cref{sec:invariant1}}
  \label{lemma:fidelity-maybeeta}
\end{theorem}
\todo{should we introduce W/eta as prev section W/beta?}

@@

\begin{theorem}[Fidelity with \linkbeta]
  The introduction of \linkbeta guarantees \fullref{prop:fidelity-recovery}
  if \Uo{} fails outside \llambda.
\end{theorem}
\todo{should we introduce W/llam as prev section W/beta and W/eta?}

@@

\emph{The approach presented in this paper}
provides a third option that addresses all the concerns
mentioned earlier. It capitalizes on the benefit of not requiring to fully
implement
the unification algorithm of the object language. Instead, it employs the
unification capabilities of the meta language, facilitated by the various links
%we establish
to manage ``problematic'' subterms. As a result of this choice our encoding takes
advantage of indexing data structures and mode analysis for clause filtering.
It it worth mentioning that we only replace terms with variables only
when it is strictly needed, leaving the rest of the term structure intact
and hence indexable by the meta language logic programming engine.
Moreover, the unification process we obtain is ready to take
advantage of potential improvements to the programming engine,
such as tabled search, and apply forms of static analysis for
the meta language, such as determinacy, to the object language.
\todo{mention preliminar experiment show that our prolog is 2x faster than the Coq one} 
Finally, our approach is flexible enough to accommodate different strategies
and heuristics to handle terms outside the pattern fragment, and
it is not tightly coupled with CIC.
